Data Exploration

### 2019-01-31 src/data_exploration.Rmd
rerun correlations etc on background10k pm

and subset into background and presences
```{r}
presab <- read.csv("../output/bio/presab.csv", header = TRUE)
presence <- subset(presab, occurrence == "1")
background <- subset(presab, occurrence == "0")
```

@@

add nafo region and gear type into the mix

@@

Interesting that there is a point in 1C - this is outside Canadian waters remove from the dataset
```{r}
presab <- presab[!(presab$nafo_zone == "1C" & presab$occurrence == "1"), ]
write.csv(presab, "../output/bio/presab.csv", row.names = FALSE)
presence <- presence[!(presence$nafo_zone == "1C"), ]
```

@@

ggplot(bottom_trawl, aes(x = ssh_surface, colour = gear)) + geom_density(na.rm = TRUE) + geom_density(data=bottom_trawl_alfredo_03, na.rm = TRUE) + geom_density(data=bottom_trawl_campelen_14, na.rm = TRUE) + geom_density(data=bottom_trawl_campelen_1800, na.rm = TRUE) + geom_density(data=bottom_trawl_campelen_21, na.rm = TRUE) + geom_density(data=bottom_trawl_cosmos_2600, na.rm = TRUE) + geom_density(data=bottom_trawl_western_IIA, na.rm = TRUE) + geom_density(data=unknown, na.rm = TRUE) + geom_density(data=vertical_plankton_tow, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_gear_plots/ssh_gear.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

>>>>

and subset into background and presences
```{r}
presab <- read.csv("../output/bio/presab_10k.csv", header = TRUE)
presence <- subset(presab, occurrence == "1")
background <- subset(presab, occurrence == "0")
```

@@

add nafo region and gear type into the mix CANT!!

@@

Interesting that there is a point in 1C - this is outside Canadian waters remove from the dataset
```{r}
presab <- presab[!(presab$nafo_zone == "1C" & presab$occurrence == "1"), ]
write.csv(presab, "../output/bio/presab_10k.csv", row.names = FALSE)
presence <- presence[!(presence$nafo_zone == "1C"), ]
```

@@

ggplot(bottom_trawl, aes(x = ssh_surface, colour = gear)) + geom_density(na.rm = TRUE) + geom_density(data=bottom_trawl_alfredo_03, na.rm = TRUE) + geom_density(data=bottom_trawl_campelen_14, na.rm = TRUE) + geom_density(data=bottom_trawl_campelen_1800, na.rm = TRUE) + geom_density(data=bottom_trawl_campelen_21, na.rm = TRUE) + geom_density(data=bottom_trawl_cosmos_2600, na.rm = TRUE) + geom_density(data=bottom_trawl_western_IIA, na.rm = TRUE) + geom_density(data=unknown, na.rm = TRUE) + geom_density(data=vertical_plankton_tow, na.rm = TRUE)
dev.copy(png,"../output/env/env_by_gear_plots/ssh_gear.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```
XXXSAM FROM HERE - NEED TO ADD PLOTS TO RESULTS DOC THEN CONTINUE
